\papertitle

### 2017-02-20 paper/paper.tex
Added the ways of windows
Can synthesize arbitrary prolate spheroidal window using parameter W and length
N.

Can approximate any window by a once-differentiable sum-of-cosines window via
constrained least-squares.

This new window has been incorporated into the measurements. It performs poorly
in noise, probably due to the extremely large main lobe. It performs the best at
obtaining the parameters of two components in mixture (in no noise). Perhaps
using more bins around the maximum will improve estimation in the noisy case. It
would be interesting to see how the estimation accuracy changes a

@@

%\newpage
\nocite{*}
\bibliographystyle{IEEEbib}
\bibliography{paper} % requires file DAFx17_tmpl.bib

>>>>

The family of parametric windows whose construction is based on functions
proposed by Slepian et al. maximimzing the energy in a given bandwidth can be
tuned to have extremely low side-lobes, at the expense of main-lobe width.
Differentiation of these window functions may be possible but is not as
straight-forward as differentiation of the sum-of-cosine windows. Furthermore,
the windows do not generally have end-points equal to 0. Motivated by this, and
the desire to approximate aribtrary windows using sums of cosines leads us to
the design of high-performance windows (e.g., with extremely low side-lobes) by
approximation.

@@

%\newpage
\nocite{*}
\bibliographystyle{IEEEbib}
%\bibliography{paper} % requires file DAFx17_tmpl.bib
